### 2024-10-01 project3/draft.tex
new

Table~\ref{tab3:transfer_learning_results} summarizes the MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
The last row shows the performance of training without TL on the target task.
The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from different source tasks to the target task, and it is consistent with the observations from the learning curves.
These numerical results highlight the importance of selecting appropriate TL strategies based on the similarity between the source and target tasks. 
Even when the source and target contracts are substantially different, TL via fine-tuning can still offer performance improvements over training from scratch. 
The ability to transfer general feature representations underscores the value of TL in dynamic hedging of VAs. 
It enables more efficient training of metamodels and reduces computational burden for hedging new VA products. 
Therefore, it is still worthwhile to transfer information from GMMB contracts when developing metamodels for more complex VA contracts with limited simulation data.

>>>>

Table~\ref{tab3:transfer_learning_results} summarizes the true MSEs of the LSTM metamodels trained using different TL methods across various source tasks.
The calculations are based on the metamodel predictions and the approximate true contract losses with $100,\!000$ inner replications.
The last row shows the performance of training without TL on the target task.
The results demonstrate the effectiveness of fine-tuning and layer freezing in transferring knowledge from different source tasks to the target task, and it is consistent with the observations from the learning curves.
These numerical results highlight the importance of selecting appropriate TL strategies based on the similarity between the source and target tasks. 
Even when the source and target contracts are substantially different, TL via fine-tuning can still offer performance improvements over training from scratch. 
The ability to transfer general feature representations underscores the value of TL in dynamic hedging of VAs. 
It enables more efficient training of metamodels and reduces computational burden for hedging new VA products. 
Therefore, it is still worthwhile to transfer information from GMMB contracts when developing metamodels for more complex VA contracts with limited simulation data.
